Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-12 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
paper: conclusion

We have seen that exact restricted isometry constants can be computed not only via total enumeration but also by solving a mixed integer semidefinite program. Because of this exactness result, the new problem can drastically
improve the bounds computed by the semidefinite relaxations proposed in \cite{Asp08} and \cite{Asp07}, but this comes at the cost of a much higher complexity of computation, at least in comparison to \cite{Asp07}. We could only 
solve these problems for relatively small instances, but this might change with sufficient advances in the area of mixed integer semidefinite programming, especially with the addition of special cutting planes, which proved to be 
the main enhancement needed to make mixed integer linear solvers as fast as they are today. Also special heuristics and branching rules could improve the performance of the branch-and-bound-algorithm and allow us to solve bigger 
instances of the proposed MISDP.

>>>>

\noindent
This paper shows that exact values of restricted isometry constants can be
computed via mixed-integer semidefinite programming. Although the used
matrices are necessarily small, we can significantly improve the bounds
computed by the semidefinite relaxations proposed in \cite{Asp08} and
\cite{Asp07}. Moreover, the results of this paper can be used to design
further approximations of the RIP, which might also be applicable for
larger matrices. On the negative side, the running time of the mixed-integer
semidefinite approach is significantly larger than the relaxation
of~\cite{Asp07}. On the positive side, it is faster and/or uses less memory
than the relaxation of \cite{Asp08} and it computes optimal constants!

For the future, the hope is that with the advancement of solving techniques
for mixed-integer semidefinite programs, the sizes of the matrices can be
significantly increased. The components to be improved include cutting
planes, primal heuristics, and branching rules.
